---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# corgraph

<!-- badges: start -->
<!-- badges: end -->

The goal of corgraph is to add a visual component that complements the `cor.test()` function. 

## Installation

You can install the released version of corgraph from [github](https://github.com/BuggyBDrizzy/corgraph) with:

``` r
devtools::install_github("https://github.com/BuggyBDrizzy/corgraph")
```

## Example

This is a basic example which shows you how to correlate two vectors:

```{r example}
library(corgraph)
cortest(datasource = Date, var2 = "Total_N", cormethod = "pearson", verbose = TRUE)
```


#### Development explanation

1. First we used `library(devtools)` to be able to help construct files 
2. `create_package()` initializes the creation
3. `use_r()` creates the necessary .R files
4. Ensure `roxygen2` comment skeleton is used to format properly
5. `uses_mit_license()` adds the necessary license so that people are able to download and use the package
6. document() command is a handy function for documenting your files without having to do it manually
7. `load_all()` roughly simulates what happens when a package is installed and loaded with `library`
8. `use_test()` will create our test file where we use any necessary `test_that()` functions
9. `check()` checks for warnings and errors
10. `use_readme_rmd()` creates an .Rmd to show basic functionality. Rmd files allow you to insert code chunks from R
11. `use_vignette()` creates a file that you can use to show functionality of your functions and package as a whole




