---
title: "cortest"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{cortest}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(corgraph)
```

#### This is a short look at the included dataset, `Date`:

```{r}

head(Date, n = c(5,11))

```



#### This is how to use the `cortest()` function using the default `Date` object:

```{r}

cortest(datasource = Date, var2 = "Total_N", cormethod = "pearson", verbose = TRUE)

```

#### You will want to pass your own tibble or dataframe object to the function, while specifying the two variables you would like to correlate. Here is an example using the `starwars` dataset. 

```{r}

cortest(datasource = dplyr::starwars, var1 = "height", var2 = "mass", cormethod = "pearson", verbose = TRUE)

```


#### Removing the confidence interval:

```{r}

cortest(datasource = dplyr::starwars, var1 = "height", var2 = "mass", cormethod = "pearson", verbose = TRUE, interval = FALSE)

```


#### For non-parametic data, use kendall or spearman as your `method`:

```{r}

cortest(datasource = dplyr::starwars, var1 = "height", var2 = "mass", cormethod = "kendall", verbose = TRUE, interval = FALSE)

```



